Generating Correlated Data for Omics Simulation

### 2025-02-06 manuscript/paper.qmd
Update affiliations

---
title: Generating Correlated Data for Omics Simulation
author:
    - name: "Jianing Yang"
      orcid: 0000-0002-2048-9398
      affiliations:
        - name: "Institute for Translational Medicine and Therapeutics, University of Pennsylvania"
        - name: "Chronobiology and Sleep Institute, University of Pennsylvania"
    - name: "Gregory R. Grant"
      orcid: 0000-0002-0139-7658
      affiliations:
        - name: "Institute for Translational Medicine and Therapeutics, University of Pennsylvania"
    - name: "Thomas G. Brooks"
      orcid: 0000-0002-6980-0079
      affiliations:
        - name: "Institute for Translational Medicine and Therapeutics, University of Pennsylvania"
editor: 
  markdown: 
    wrap: sentence
execute:
  echo: false
  cache: true
format:
  html:
    toc: true
    toc-expand: true
bibliography: references.bib
---
## Abstract

>>>>

---
title: Generating Correlated Data for Omics Simulation
author:
    - name: "Jianing Yang"
      orcid: 0000-0002-2048-9398
      affiliations:
        - name: "Chronobiology and Sleep Institute, University of Pennsylvania"
    - name: "Gregory R. Grant"
      orcid: 0000-0002-0139-7658
      affiliations:
        - name: "Department of Genetics, University of Pennsylvania"
    - name: "Thomas G. Brooks"
      orcid: 0000-0002-6980-0079
      affiliations:
        - name: "Institute for Translational Medicine and Therapeutics, University of Pennsylvania"
editor: 
  markdown: 
    wrap: sentence
execute:
  echo: false
  cache: true
format:
  html:
    toc: true
    toc-expand: true
bibliography: references.bib
---
## Abstract
